**Title:** Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system

### 2019-05-28 output/review/vaccine-review-response-2.Rmd

---
title: "Reviewer Response"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

Dear Dr. Orenstein,

Thank you for sending review reports for our manuscript.

We have revised the paper in light of the reviewers’ comments. In particular, we have revised the tables for clarity, and improved their captioning.

We enclose a revised version of the manuscript (clean and with tracked changes), which addresses the reviewers' comments and suggestions. The reviewers' comments are shown below with our response to each comment in italics.

We hope that the manuscript is now suitable for publication in Vaccine.

@@

2. I like to "follow the data" within the paper but found the tables to be nearly impossible to follow; in fact, I still don't really understand them because of how things are labeled and presented. I apologize if I am just missing something, but I have no idea to what the "Yes" and "No" refer. I have reviewed a lot of papers and if I have to spend this much time trying to decipher the tables, then there is likely a better way to present the data. For example, in Table 1, there is a heading "Death due to TB (in those who died)"; below that are the rows "Yes" and "No". I thought that the yes-no referred to whether they died of TB, but then I got to Table 3 where the numbers next to "Death due to TB (in those who died)" are used. Sorry but I just cannot follow it - makes no sense to me. Perhaps the problem is how things are labeled and formatted but please try to make this easier to understand. In addition the format {% all cases}(% complete within vaccine status)[complete within category] is also very confusing.

*We are sorry that the table formatting was difficult to interpret. We have added the following to the table captions for tables 3 and 4 to clarify the cases and cases with outcome columns:*

*"Cases represents all notifications with complete data and a given BCG status, regardless of outcome. Cases with outcome is similarly defined but includes only cases with the specified outcome."*

*We have also clarified the definition of sputum spear status in Table 1 and UK birth status in Table 2.*

*We agree that the use of the {% all cases}(% complete within vaccine status)[complete within category] structure in Table 1 and Table 2 adds complexity but feel that this is justified as missing data is an important consideration for this study. We would welcome suggestions for improvements.*

### 2019-05-28 output/Paper.Rmd
second vaccine review changes

@@

demo_sum_bcg$`Demographic Characteristics` <- stringr::str_replace(demo_sum_bcg$`Demographic Characteristics`, "deprived\\)", "deprived\\)\\*")

>>>>

outcome_sum$`Demographic Characteristics` <- stringr::str_replace(outcome_sum$`Demographic Characteristics`, " - positive", "")

@@

demo_sum_bcg$`Demographic Characteristics` <- stringr::str_replace(demo_sum_bcg$`Demographic Characteristics`, "deprived\\)", "deprived\\)\\*")
demo_sum_bcg$`Demographic Characteristics` <- stringr::str_replace(demo_sum_bcg$`Demographic Characteristics`, "UK born", "UK birth status")
